Preventing runtime errors of Redis at compile time

### 2015-11-19 paper.tex
Added one simple notice.
draft

\authorinfo{Person 1 \and Person 2}
{\makebox{A Department} \\
\makebox{A University}  \\
\makebox{A Place, AS 12345}}
{\{person1,person2\}@cs.auniv.edu}

@@

\subsection{Problems}

@@

\section{Discussions}
\paragraph{Syntax}
No one could ignore the glaring shortcoming of the syntax, which occurs mainly
 in two places: symbol singletons and indexed monad. We are hoping that these
 issues could be solved with future syntactic extensions.

@@

In Hedis such command could easily be expressed with lists of
 \mintinline{haskell}{ByteString}s. But in Edis, things escalate quickly, as
 the keys and values will have to be expressed with heterogeneous
 lists\cite{hetero}, which would be pratically infeasible, considering the cost,
 if not impossible.

@@

Redis provides transactions, another context for executing commands.
Redis trasanctions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served in the middle.\footnotemark In contrast, we cannot make such
 guarantee in the ordinary context, which may destroy the assertions we made
 in types.

@@

\section{Conclusion and Related Work}
\paragraph{Acknowledgements}

>>>>

\authorinfo{Ting-Yan Lai}
{\makebox{Institute of Computer Science and Engineering} \\
\makebox{National Chiao Tung University, Taiwan}}
{banacorn.cs03g@nctu.edu.tw}

\authorinfo{Tyng-Ruey Chuang \and Shin-Cheng Mu}
{\makebox{Institute of Information Science} \\
\makebox{Academia Sinica, Taiwan}}
{\{trc,scm\}@iis.sinica.edu.tw}

@@

\section{Motivation}

@@

\section{Discussions}
\paragraph{Syntax}
No one could ignore the glaring shortcoming of the syntax, which occurs mainly
 in two places: \emph{symbol singletons} and \emph{indexed monad}. We are hoping
 that these issues could be solved with future syntactic extensions.

@@

In Hedis such command could easily be expressed with lists of
 \mintinline{haskell}{ByteString}s. But in Edis, things escalate quickly, as
 the keys and values will have to be expressed with \emph{heterogeneous
 lists}\cite{hetero}, which would be pratically infeasible, considering the cost,
 if not impossible.

@@

Redis also provides \emph{transactions}, another context for executing commands.
Redis trasanctions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served \textbf{in the middle}.\footnotemark In contrast, we cannot make such
 a guarantee in the ordinary context, which may destroy the assertions we made
 in types.

@@

\section{Related Work}

While Redis can be viewed as a non-relational database system (although Redis
 seems reluctant to admit this in recent years), there also similar goals on
 relational database systems, trying to achieve a safer database interface by
 making them statically checked.
 \emph{HaskellDB}\cite{haskelldb}\cite{haskelldbimproved} expresses quries
 with relational algebra-like combinators, wrapped in phantom types. Or as
 examples, at first to demonstrate the power of dependent types in
 Agda\cite{pi}, and then with singletons in Haskell\cite{singletons}.

\section{Conclusions}

We have shown that how a embedded DSL with variable-bindings could be expressed
 in types and statically checked. With recent extensions to the language,
 Haskell is becoming more and more capable of dependently-typed programming, and
 it's not that scary as many (including me) would have thought.

\paragraph{Acknowledgements}
This material is based upon work supported by Institute of Information Science,
Academia Sinica under the Summer Internship Program of 2015.
